---
title: "01_119_rmd"
author: "Mark Niemann-Ross"
date: "2/10/2020"
output: html_document
---
Use rmd for documentation	
Rmd is an R version of markdown, a common format for writing documentation. 
Learning to create reproducible and documented course is essential for data scientists.

Check out Ray Villalobos "Up and Running with Markdown"

if you're using Rstudio - it's installed
if you're not using rstudio, install.packages("rmarkdown")

```{r}
avector <- c(1:5)

print(avector)
```

change to {r, echo = FALSE}
```{r, echo=FALSE}
avector <- c(1:5)

print(avector)
```

change to {r, include=FALSE}
```{r, include=FALSE}
avector <- c(1:5)

```

removes all from view, then use that code in a later code block
```{r}
print(avector)
```

what languages are supported by knitr?

```{r}
names(knitr::knit_engines$get())
Sys.which("python")
```

# add python.reticulate = false...

```{python, python.reticulate = FALSE}
x = 42 * 2
print("python", x) 
```

Under windows, this won't work...
```{bash}
print "this is bash"
```

# Why not?

```{r}
Sys.which("bash") 
```
Sys.which comes up empty on windows because bash not installed

